\section{Tool and Techniques Evaluation}

The use of pair programming for our project has worked well sometimes, the quality of the code is better than code written by one person, which often requires more refactoring than the code written when pair programming.
This has at least been the case for us. 
We need to be better at using pair programming as it is specified, which means that the person overlooking the other programmer should not have his own computer turned on aswell, we think this would increase the quality further. 

For version control we used git which resulted in us being able to work in parallel and just merge any conflicts if they ever occur.
We make branches and pull requests to control the workflow and making sure that any work being done using git will get peer reviewed, as it will not be pushed to the master branch unless a pull request has been made ensuring that someone has reviewed it.
Before using git we tried using Sharelatex, which is like Google Docs but uses \LaTeX, this worked okay but, our review process was lacking, therefore we decided to make the change to Github for the added functionality in using pull requests etc. 
This requires an explicit action before text is in the master, therefor forcing the review process. 

Peer review work very well for us as the quality of everything is a lot better than if we did not use it, it also helps us spreading the knowledge of all the different parts of the project, since more people will have the same parts of the project.

We also decided to review the result of previous iterations, if new requirements appear we can go back and review different parts to ensure they are up to date with the new requirements.
We delete useless things, and ensure that everyone understand everything written, which is exactly what we wanted from it.