\chapter{Evaluation of practices}
With the SOE course we have taken a close look at the processes we have used, for this semester, and the ones we have adapter from our use on previous semesters.
The most notable of these is Scrum, we have used a relaxed version of Scrum, as there is not a product owner available. 
The primary advantage in Scrum for us have been the Scrum board, and the mindset of (bi-)weekly sprints.
This have kept our group in sync with each other, and have kept us on the right track. 
However we have moved so far from the original Scrum model, we would like to move back closer to it.
Being better to have proper sprint meetings, harder deadline, and a better backlog. 

A significant problem in project group have been that the elective courses have taken up a lot of time, sometimes causing to group to not proper stand-up meetings for 2 days in a row. 
This problem was in part solved by doing work as two sub-groups. 

A practice we have had much use of is pair programming, however from time to time the group members had a hard time focusing on the task at hand. 
Mainly the non-writing part of the pair, to combat this we should be better at moving away from distractions, such as their own laptop, or out of the group room. 

Finally we shouldn't be nervous about making big changes, especially early on, to improve the quality of our work. 
This might mean that we remove something one or more group members have spent a lot of time on, this is also why it can be hard to remove. 
